---
title: "Simulation_Update-8-22-16"
author: "Sadie Wisotsky"
date: "August 22, 2016"
output: 
  word_document: 
    fig_caption: yes
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(jsonlite)
library(ggplot2)
library(knitr)
library(stringr)
library(reshape2)
```

```{r branch lengths, echo=FALSE, include=FALSE}
require("tidyr")
#Right now these are just he BUSTED-SRV branch lengths
branch_length <- function(cur.dir){
  jsons <- list.files(path = cur.dir,
                      pattern = '*.json')
  
  #create empty data.frame with variable names
  
  df = read.table(text="", col.names = c("Branch", "File", "length.SRV","length.BUSTED"))
  for (i in  seq(from=1, to=length(jsons), by=2)){
    
    
    FILE = jsons[i]
   
    
    if(grepl("SRV", jsons[i])){
      method = "SRV"
      filepath = paste(cur.dir,jsons[i], sep="")
    
    test = fromJSON(filepath)
      tree_string = test$fits$`Unconstrained model`$`tree string`
 
          x= tree_string %>% str_replace_all("\\(",":") %>% str_replace_all("\\)",":") %>%
            str_replace_all(",",":") %>% str_split(":")
    x= unlist(x)
    x =x[x !=""]
    br_len = matrix(x,ncol = 2,  byrow = T)
      
    }
    length.srv = br_len[,2]
    
    if(grepl("SRV",jsons[i+1])==FALSE){
      method = "BUSTED"   
      filepath = paste(cur.dir,jsons[i+1], sep="")
    
    test = fromJSON(filepath)
          tree_string = test$fits$`Unconstrained model`$`tree string`

      x= tree_string %>% str_replace_all("\\(",":") %>% str_replace_all("\\)",":") %>% 
        str_replace_all(",",":") %>% str_split(":")
    x= unlist(x)
    x =x[x !=""]
    br_len = matrix(x,ncol = 2,  byrow = T)
      
    }
    length.BUSTED = br_len[,2]
      for(k in seq(from=1,to=length(br_len)/2)){
      df[nrow(df)+1,]=c(br_len[k,1], FILE, length.srv[k],length.BUSTED[k])
      }
  }
  #df_wide = spread(df,File, length)
    return(df)
}
```

```{r more functions, echo = FALSE, include=FALSE}
#adds significant categories and normalizes alphas
process.dat <- function(dat, redo.alphas = TRUE){
### Add sig categories
  dat= cbind(dat,p.cat=cut(dat$BUSTED.P,breaks=c(-Inf,0.05,Inf),
                            labels = c("S V B", "NS V B")))
  dat= cbind(dat,p.srv.cat=cut(dat$BUSTED.SRV.P,breaks=c(-Inf,0.05,Inf),
                                labels = c("S V BSRV", "NS V BSRV")))
###rearrange alphas
  if(redo.alphas==TRUE){
    normalize = dat$SRV.alpha1.MLE*dat$SRV.alpha1.prop + 
                dat$SRV.alpha2.MLE*dat$SRV.alpha2.prop+ 
                dat$SRV.alpha3.MLE*dat$SRV.alpha3.prop
      
    
    dat = cbind(dat,true.alpha1 = dat$SRV.alpha1.MLE/normalize,
            true.alpha2 = dat$SRV.alpha2.MLE/normalize,
            true.alpha3 = dat$SRV.alpha3.MLE/normalize)
  }
  else{
    #sets the true.alpha values to just the standard MLE 
    #makes the rest of the stream line analysis easier. 
    #it's either this or make you specify alpha variables in later steps...
    dat = cbind(dat,true.alpha1 = dat$SRV.alpha1.MLE,
                true.alpha2 = dat$SRV.alpha2.MLE,
                true.alpha3 = dat$SRV.alpha3.MLE)  }
}



```

```{r summary stats, echo = FALSE, include=FALSE}
# here's where you'd have to start specifying other alphas 
# returns a list of statistics generated from the boxplot function 
# note the omega3 value here is from BUSTED SRV 
# not the omega3 from BUSTED for the same file
box.sum.stats <- function(dat, subset = NULL){
  omega3 = boxplot(
    dat$BUSTED.SRV.omega3.MLE ~ dat$p.cat + dat$p.srv.cat, data = dat, 
    subset = subset, plot = FALSE
  )
  
  alpha1 = boxplot(
    dat$true.alpha1 ~ dat$p.cat + dat$p.srv.cat, data = dat,
    subset = subset, plot = FALSE
  )

  alpha2 = boxplot(
    dat$true.alpha2 ~ dat$p.cat + dat$p.srv.cat, data = dat,
    subset = subset, plot = FALSE
  )

  alpha3 = boxplot(
   dat$true.alpha3 ~ dat$p.cat + dat$p.srv.cat, data = dat,
   subset = subset,plot = FALSE
  )
  results <- list(omega3 =omega3, alpha1 = alpha1,alpha2= alpha2, alpha3 = alpha3)
  return(results)
}

gen.tables <- function(box.stats){
  catnames = c("Sel for both", "No Sel for BUSTED", "No Sel for SRV", "No Sel for both")
  statlist = c("lower whisker","lower hinge","median","upper hinge","upper whisker", "number of files")
  omega3 = box.stats$omega3$stats
  omega3 = rbind(omega3,box.stats$omega3$n)
  colnames(omega3) = catnames
  rownames(omega3) = statlist
  
  alpha1 = box.stats$alpha1$stats
  alpha1 = rbind(alpha1,box.stats$alpha1$n)
  colnames(alpha1) = catnames
  rownames(alpha1) = statlist
  
  alpha2 = box.stats$alpha2$stats
  alpha2 = rbind(alpha2,box.stats$alpha2$n)
  colnames(alpha2) = catnames
  rownames(alpha2) = statlist
  
  alpha3 = box.stats$alpha3$stats
  alpha3 = rbind(alpha3,box.stats$alpha3$n)
  colnames(alpha3) = catnames
  rownames(alpha3) = statlist
  
   results <- list(omega3 =omega3, alpha1 = alpha1,alpha2= alpha2, alpha3 = alpha3)
  return(results)
}

gen.summary.o.tabs <- function(dat){
  omega1.busted =  summary(dat$BUSTED.omega1.MLE)
  omega1.srv = summary(dat$BUSTED.SRV.omega1.MLE)
  omega2.busted =summary(dat$BUSTED.omega2.MLE)
  omega2.srv = summary(dat$BUSTED.SRV.omega2.MLE)
  omega3.busted =summary(dat$BUSTED.omega3.MLE)
  omega3.srv = summary(dat$BUSTED.SRV.omega3.MLE)
  results = rbind(omega1.busted,omega1.srv,omega2.busted,omega2.srv,omega3.busted,omega3.srv)
  return(results)
}
gen.summary.a.tabs <- function(dat){
  
  alpha1.srv = summary(dat$SRV.alpha1.MLE)
  alpha2.srv = summary(dat$SRV.alpha2.MLE)
  alpha3.srv = summary(dat$SRV.alpha3.MLE)
  results = rbind(alpha1.srv, alpha2.srv,alpha3.srv)
  return(results)
}
```

```{r gen sig table, include=FALSE}
gen.sig.table <- function(dat){
  require("xtable")
  library("xtable")
  
  under.sel.busted = which(dat$BUSTED.P<=0.05)
  under.sel.srv = which(dat$BUSTED.SRV.P<=0.05)
  if( length(under.sel.srv) == 0){
    
    mat = matrix( rep(0),nrow=length(dat$BUSTED.P),ncol = 2,
                  dimnames= list(1:length(dat$BUSTED.P),
                                 c("BUSTED", "BUSTED-SRV")))
    mat[under.sel.busted,1] = 1
    mat[under.sel.srv,2] = 1 
    sel.tab = table(mat[,1],mat[,2], dnn = colnames(mat))
    #row.names(sel.tab) = c("Selection:BUSTED")
    #colnames(sel.tab) = c("No Selection:BUSTED+SRV")
    Sel.Prop =prop.table(sel.tab)
    test.table = xtable(Sel.Prop)
    #print.xtable(test.table, type = "html")
    #print(kable(test.table))
    #return("All alignments are not significant according to BUSTED+SRV")
  }
  else if( length(under.sel.busted) == 0){
    
    mat = matrix( rep(0),nrow=length(dat$BUSTED.P),ncol = 2,
                  dimnames= list(1:length(dat$BUSTED.P),
                                 c("BUSTED", "BUSTED-SRV")))
    mat[under.sel.busted,1] = 1
    mat[under.sel.srv,2] = 1 
    sel.tab = table(mat[,1],mat[,2], dnn = colnames(mat))
    #row.names(sel.tab) = c("No Selection:BUSTED")
    #colnames(sel.tab) = c("Selection:BUSTED+SRV")
    Sel.Prop =prop.table(sel.tab)
    test.table = xtable(Sel.Prop)
    #print.xtable(test.table, type = "html", file="sel-table.html")
    #return("All alignments are not significant according to BUSTED")
  }
  else {
    mat = matrix( rep(0),nrow=length(dat$BUSTED.P),ncol = 2,
                  dimnames= list(1:length(dat$BUSTED.P),
                                 c("BUSTED", "BUSTED-SRV")))
    mat[under.sel.busted,1] = 1
    mat[under.sel.srv,2] = 1 
    sel.tab = table(mat[,1],mat[,2], dnn = colnames(mat))
    #row.names(sel.tab) = c("No Selection", "Selection")
    #colnames(sel.tab) = c("No Selection", "Selection")
    Sel.Prop =prop.table(sel.tab)
    test.table = xtable(Sel.Prop)
    #print.xtable(test.table, type = "html", file="sel-table.html")
  }
  return(Sel.Prop)
}
```

```{r NoNo data set-up, echo=FALSE}

NoNo.dat=read.csv("G:/BRC/SimResults/Five_seq/NoNo_results.csv",  as.is = T)
#NoNo.brlen = branch_length("G:/BRC/SimResults/NoNo/")
NoNo.process.dat = process.dat(NoNo.dat)
NoNo.melt.dat=melt(NoNo.process.dat[,c(1,31:35)])
NoNo.sum.stat = box.sum.stats(NoNo.process.dat)
NoNo.bias = NoNo.dat[,c(1,17:18,21:22,4:5)]

```



#Simulation with no SRV and no selection



```{r set up truth table NoNo, echo=FALSE}

truth.NoNo = matrix(c(1,1,1,0.1,0.5,1,0.333,0.333,0.3337000000000001,0.5,0.25,0.25),nrow = 6, ncol= 2)
colnames(truth.NoNo)= c(" True Rates", "True Weights")
rownames(truth.NoNo) = c("alpha 1","alpha 2","alpha 3", "omega 1", "omega 2", "omega 3")
```


```{r summary stats table NoNo, echo = FALSE}
true.omegas.rates = c(truth.NoNo[4,1],truth.NoNo[4,1],truth.NoNo[5,1],truth.NoNo[5,1],truth.NoNo[6,1],truth.NoNo[6,1])

sum.table.omegas =gen.summary.o.tabs(NoNo.process.dat)[,3:4] %>% cbind("True Rates" = true.omegas.rates) %>% cbind("Estimated Weight" = cbind( NoNo.dat$BUSTED.omega1.prop, NoNo.dat$BUSTED.SRV.omega1.prop,NoNo.dat$BUSTED.omega2.prop,NoNo.dat$BUSTED.SRV.omega2.prop,NoNo.dat$BUSTED.omega3.prop,NoNo.dat$BUSTED.SRV.omega3.prop)  %>% apply(2,mean)) %>% cbind("True Weights" =c(truth.NoNo[4,2],truth.NoNo[4,2],truth.NoNo[5,2],truth.NoNo[5,2], truth.NoNo[6,2], truth.NoNo[6,2]))

sum.table.alphas = gen.summary.a.tabs(NoNo.process.dat)[,3:4] %>% cbind("True Rates"=c(truth.NoNo[1:3,1])) %>% cbind("Estimates Weight"=cbind(NoNo.process.dat$SRV.alpha1.prop,NoNo.process.dat$SRV.alpha2.prop,NoNo.process.dat$SRV.alpha3.prop) %>% apply(2,mean)) %>% cbind("True Weights" = truth.NoNo[1:3,2])

sum.table.NoNo = rbind(sum.table.omegas,sum.table.alphas)
```

`r kable(sum.table.NoNo,"markdown", caption = "Summary Table for Simulation with No Selection and No SRV")`


```{r, echo = FALSE}

q = cbind("Truth"=as.numeric(sum.table.NoNo[1:6,3]),variable=c("BUSTED.omega1.MLE","BUSTED.SRV.omega1.MLE","BUSTED.omega2.MLE","BUSTED.SRV.omega2.MLE","BUSTED.omega3.MLE", "BUSTED.SRV.omega3.MLE")) %>% as.data.frame()
NoNo.bias %>% melt() %>% ggplot(aes(value))+geom_histogram() +facet_wrap(~variable, scales = "free", ncol = 2)+ geom_vline(data = q,aes(xintercept = as.numeric(Truth)),color = "red") + ggtitle("Distribution of Omega Rates For No Selection and SRV")

```

The histograms below show the distribution of the alpha rates

```{r histograms NoNo, echo = F, warning=F}
truth.alpha=c(truth.NoNo[1:3,1])
c = cbind(as.numeric(truth.alpha),variable=c("true.alpha1","true.alpha2","true.alpha3")) %>% as.data.frame()
ggplot(NoNo.melt.dat, aes(value))+geom_histogram()+facet_wrap(~variable, scales = "free_x") + geom_vline(data = c, aes(xintercept = truth.alpha), color = "red")+ ggtitle("Distribution of Alpha Rates For No Selection and SRV")

```

A plot of the p values for BUSTED versus BUSTED-SRV. THis allows us to compare the results of the two analysis to each other. 

```{r p plot NoNo}
ggplot(NoNo.process.dat, aes(x= BUSTED.P,y=BUSTED.SRV.P))+geom_point()+geom_vline(xintercept = 0.05,color="red")+geom_hline(yintercept = 0.05, color = 'red')


ggplot(NoNo.process.dat, aes(x= BUSTED.P,y=BUSTED.SRV.P))+geom_bin2d(binwidth=c(0.01,0.01))+geom_vline(xintercept = 0.05,color="red")+geom_hline(yintercept = 0.05, color = 'red')
```

```{r sel table NoNo, echo = FALSE}
kable(gen.sig.table(NoNo.dat))
```

##plots without the 3 major outliers:

```{r, echo = FALSE}
 NoNo.dat.no.outs=NoNo.process.dat[-c(65,21),]
```



```{r set up truth table1 NoNo, echo=FALSE}

truth.NoNo = matrix(c(1,1,1,0.1,0.5,1,0.333,0.333,0.3337000000000001,0.5,0.25,0.25),nrow = 6, ncol= 2)
colnames(truth.NoNo)= c(" True Rates", "True Weights")
rownames(truth.NoNo) = c("alpha 1","alpha 2","alpha 3", "omega 1", "omega 2", "omega 3")
```


```{r summary stats table 1, echo = FALSE}
true.omegas.rates = c(truth.NoNo[4,1],truth.NoNo[4,1],truth.NoNo[5,1],truth.NoNo[5,1],truth.NoNo[6,1],truth.NoNo[6,1])

sum.table.omegas =gen.summary.o.tabs(NoNo.dat.no.outs)[,3:4] %>% cbind("True Rates" = true.omegas.rates) %>% cbind("Estimated Weight" = cbind( NoNo.dat.no.outs$BUSTED.omega1.prop, NoNo.dat.no.outs$BUSTED.SRV.omega1.prop,NoNo.dat.no.outs$BUSTED.omega2.prop,NoNo.dat.no.outs$BUSTED.SRV.omega2.prop,NoNo.dat.no.outs$BUSTED.omega3.prop,NoNo.dat.no.outs$BUSTED.SRV.omega3.prop)  %>% apply(2,mean)) %>% cbind("True Weights" =c(truth.NoNo[4,2],truth.NoNo[4,2],truth.NoNo[5,2],truth.NoNo[5,2], truth.NoNo[6,2], truth.NoNo[6,2]))

sum.table.alphas = gen.summary.a.tabs(NoNo.dat.no.outs)[,3:4] %>% cbind("True Rates"=c(truth.NoNo[1:3,1])) %>% cbind("Estimates Weight"=cbind(NoNo.dat.no.outs$SRV.alpha1.prop,NoNo.dat.no.outs$SRV.alpha2.prop,NoNo.dat.no.outs$SRV.alpha3.prop) %>% apply(2,mean)) %>% cbind("True Weights" = truth.NoNo[1:3,2])

sum.table = rbind(sum.table.omegas,sum.table.alphas)
```

`r kable(sum.table,"markdown")`

Here we can see that the mean estimated omega3 value `r sum.table.omegas[5,2]` which is wildly over the true value of 1. This is what we'd expect to see as BUSTED does not account for synonymous rate variation and we simulated with a SRV and a high alpha 3 rate. 

```{r, echo = FALSE}

q = cbind("Truth"=as.numeric(sum.table[1:6,3]),variable=c("BUSTED.omega1.MLE","BUSTED.SRV.omega1.MLE","BUSTED.omega2.MLE","BUSTED.SRV.omega2.MLE","BUSTED.omega3.MLE", "BUSTED.SRV.omega3.MLE")) %>% as.data.frame()
q$Truth = as.numeric(sum.table[1:6,3])

NoNo.bias %>% melt() %>% ggplot(aes(value))+geom_histogram() +facet_wrap(~variable, scales = "free", ncol = 2)+ geom_vline(data = q,aes(xintercept = Truth),color = "red") + ggtitle("Distribution of Omega R")

```

The histograms below show the distribution of the alpha rates

```{r his1tograms NoNo, echo = F, warning=F}
truth.alpha=c(truth.NoNo[1:3,1])
c = cbind(as.numeric(truth.alpha),variable=c("true.alpha1","true.alpha2","true.alpha3")) %>% as.data.frame()
ggplot(NoNo.melt.dat, aes(value))+geom_histogram()+facet_wrap(~variable, scales = "free_x") + geom_vline(data = c, aes(xintercept = truth.alpha), color = "red")

```

A plot of the p values for BUSTED versus BUSTED-SRV. THis allows us to compare the results of the two analysis to each other. 

```{r p pl1ot NoNo}
NoNo.dat.no.outs%>% ggplot(aes(x= BUSTED.P,y=BUSTED.SRV.P))+geom_point()+geom_vline(xintercept = 0.05,color="red")+geom_hline(yintercept = 0.05, color = 'red')
```

```{r boxplot, echo = FALSE}
NoNo.dat.no.outs %>% group_by(p.cat,p.srv.cat)%>% select(contains("true"))%>% melt() %>% ggplot(aes(x = variable, y = value))+geom_boxplot(aes(color=interaction(p.cat,p.srv.cat)))+coord_flip(ylim = c(0,10))

```


```{r se1l table NoNo, echo = FALSE}
kable(gen.sig.table(NoNo.dat.no.outs))
```

*********************************************
#No Yes
Simulation with no selection and with a large amount of SRV. 
```{r NoYes data set-up, echo=FALSE}

NoYes.dat=read.csv("G:/BRC/SimResults/Five_seq/NoYes_results.csv",  as.is = T)
#NoYes.brlen = branch_length("G:/BRC/SimResults/NoYes/")
NoYes.process.dat = process.dat(NoYes.dat)
NoYes.melt.dat=melt(NoYes.process.dat[,c(1,31:35)])
NoYes.sum.stat = box.sum.stats(NoYes.process.dat)
NoYes.bias = NoYes.dat[,c(1,17:18,21:22,4:5)]

```

```{r remove outliers NoYes, echo = FALSE}
MLE.NoYes = NoYes.process.dat %>% select(contains("MLE")) 

NoYes.process.dat =NoYes.process.dat[-unlist(apply(MLE.NoYes, 2, FUN = function(col) which(col >9999))),]
```



```{r set up truth table NoYes, echo=FALSE}

truth.NoYes = matrix(c(0.1333333333333334,0.6666666666666667,6.666666666666668,0.1,0.5,1,0.5,0.4,0.09999999999999998,0.5,0.25,0.25),nrow = 6, ncol= 2)
colnames(truth.NoYes)= c(" True Rates", "True Weights")
rownames(truth.NoYes) = c("alpha 1","alpha 2","alpha 3", "omega 1", "omega 2", "omega 3")
```



```{r summary stats table NoYes, echo = FALSE}
true.omegas.rates = c(truth.NoYes[4,1],truth.NoYes[4,1],truth.NoYes[5,1],truth.NoYes[5,1],truth.NoYes[6,1],truth.NoYes[6,1])

sum.table.omegas =gen.summary.o.tabs(NoYes.process.dat)[,3:4] %>% cbind("True Rates" = true.omegas.rates) %>% cbind("Estimated Weight" = cbind( NoYes.dat$BUSTED.omega1.prop, NoYes.dat$BUSTED.SRV.omega1.prop,NoYes.dat$BUSTED.omega2.prop,NoYes.dat$BUSTED.SRV.omega2.prop,NoYes.dat$BUSTED.omega3.prop,NoYes.dat$BUSTED.SRV.omega3.prop)  %>% apply(2,mean)) %>% cbind("True Weights" =c(truth.NoYes[4,2],truth.NoYes[4,2],truth.NoYes[5,2],truth.NoYes[5,2], truth.NoYes[6,2], truth.NoYes[6,2]))

sum.table.alphas = gen.summary.a.tabs(NoYes.process.dat)[,3:4] %>% cbind("True Rates"=c(truth.NoYes[1:3,1])) %>% cbind("Estimates Weight"=cbind(NoYes.process.dat$SRV.alpha1.prop,NoYes.process.dat$SRV.alpha2.prop,NoYes.process.dat$SRV.alpha3.prop) %>% apply(2,mean)) %>% cbind("True Weights" = truth.NoYes[1:3,2])

sum.table.NoYes = rbind(sum.table.omegas,sum.table.alphas)
```

`r kable(sum.table.NoYes,"markdown")`

Here we can see that the mean estimated omega3 value `r sum.table.omegas[5,2]` which is wildly over the true value of 1. This is what we'd expect to see as BUSTED does not account for synonymous rate variation and we simulated with a SRV and a high alpha 3 rate. 

```{r, echo = FALSE}

q = cbind("Truth"=as.numeric(sum.table[1:6,3]),variable=c("BUSTED.omega1.MLE","BUSTED.SRV.omega1.MLE","BUSTED.omega2.MLE","BUSTED.SRV.omega2.MLE","BUSTED.omega3.MLE", "BUSTED.SRV.omega3.MLE")) %>% as.data.frame()
q$Truth = as.numeric(sum.table[1:6,3])
NoYes.bias %>% melt() %>% ggplot(aes(value))+geom_histogram() +facet_wrap(~variable, scales = "free", ncol = 2)+ geom_vline(data = q,aes(xintercept = as.numeric(Truth)),color = "red") + ggtitle("Distribution of Omega R")

```

The histograms below show the distribution of the alpha rates

```{r histograms NoYes, echo = F, warning=F}
truth.alpha=c(truth.NoYes[1:3,1])
c = cbind(as.numeric(truth.alpha),variable=c("true.alpha1","true.alpha2","true.alpha3")) %>% as.data.frame()
ggplot(NoYes.melt.dat, aes(value))+geom_histogram()+facet_wrap(~variable, scales = "free_x") + geom_vline(data = c, aes(xintercept = truth.alpha), color = "red")

```

A plot of the p values for BUSTED versus BUSTED-SRV. THis allows us to compare the results of the two analysis to each other. 

```{r p plot NoYes}
NoYes.process.dat%>% ggplot(aes(x= BUSTED.P,y=BUSTED.SRV.P))+geom_point()+geom_vline(xintercept = 0.05,color="red")+geom_hline(yintercept = 0.05, color = 'red')
```

`r kable(gen.sig.table(NoYes.process.dat), "markdown")`




********************************

#YesYes data

```{r YesYes data set-up, echo=FALSE}

YesYes.dat=read.csv("G:/BRC/SimResults/Five_seq/YesYes_results.csv",  as.is = T)
#YesYes.brlen = branch_length("G:/BRC/SimResults/YesYes/")
YesYes.process.dat = process.dat(YesYes.dat)
YesYes.melt.dat=melt(YesYes.process.dat[,c(1,31:35)])
YesYes.sum.stat = box.sum.stats(YesYes.process.dat)
YesYes.bias = YesYes.dat[,c(1,17:18,21:22,4:5)]

```

```{r set up truth table YesYes, echo=FALSE}

truth.YesYes = matrix(c(0.1333333333333334,0.6666666666666667,6.666666666666668,0.1,0.5,7,0.5,0.4,0.09999999999999998,0.5,0.3,0.2),nrow = 6, ncol= 2)
colnames(truth.YesYes)= c(" True Rates", "True Weights")
rownames(truth.YesYes) = c("alpha 1","alpha 2","alpha 3", "omega 1", "omega 2", "omega 3")
```



```{r summary stats table YesYes, echo = FALSE}
true.omegas.rates = c(truth.YesYes[4,1],truth.YesYes[4,1],truth.YesYes[5,1],truth.YesYes[5,1],truth.YesYes[6,1],truth.YesYes[6,1])

sum.table.omegas =gen.summary.o.tabs(YesYes.process.dat)[,3:4] %>% cbind("True Rates" = true.omegas.rates) %>% cbind("Estimated Weight" = cbind( YesYes.dat$BUSTED.omega1.prop, YesYes.dat$BUSTED.SRV.omega1.prop,YesYes.dat$BUSTED.omega2.prop,YesYes.dat$BUSTED.SRV.omega2.prop,YesYes.dat$BUSTED.omega3.prop,YesYes.dat$BUSTED.SRV.omega3.prop)  %>% apply(2,mean)) %>% cbind("True Weights" =c(truth.YesYes[4,2],truth.YesYes[4,2],truth.YesYes[5,2],truth.YesYes[5,2], truth.YesYes[6,2], truth.YesYes[6,2]))

sum.table.alphas = gen.summary.a.tabs(YesYes.process.dat)[,3:4] %>% cbind("True Rates"=c(truth.YesYes[1:3,1])) %>% cbind("Estimates Weight"=cbind(YesYes.process.dat$SRV.alpha1.prop,YesYes.process.dat$SRV.alpha2.prop,YesYes.process.dat$SRV.alpha3.prop) %>% apply(2,mean)) %>% cbind("True Weights" = truth.YesYes[1:3,2])

sum.table = rbind(sum.table.omegas,sum.table.alphas)
```

`r kable(sum.table,"markdown")`

Here we can see that the mean estimated omega3 value `r sum.table.omegas[5,2]` which is wildly over the true value of 1. This is what we'd expect to see as BUSTED does not account for synonymous rate variation and we simulated with a SRV and a high alpha 3 rate. 

```{r, echo = FALSE}

q = cbind("Truth"=as.numeric(sum.table[1:6,3]),variable=c("BUSTED.omega1.MLE","BUSTED.SRV.omega1.MLE","BUSTED.omega2.MLE","BUSTED.SRV.omega2.MLE","BUSTED.omega3.MLE", "BUSTED.SRV.omega3.MLE")) %>% as.data.frame()
q$Truth = as.numeric(sum.table[1:6,3])
YesYes.bias %>% melt() %>% ggplot(aes(value))+geom_histogram() +facet_wrap(~variable, scales = "free", ncol = 2)+ geom_vline(data = q,aes(xintercept = as.numeric(Truth)),color = "red") + ggtitle("Distribution of Omega R")

```

The histograms below show the distribution of the alpha rates

```{r histograms YesYes, echo = F, warning=F}
truth.alpha=c(truth.YesYes[1:3,1])
c = cbind(as.numeric(truth.alpha),variable=c("true.alpha1","true.alpha2","true.alpha3")) %>% as.data.frame()
ggplot(YesYes.melt.dat, aes(value))+geom_histogram()+facet_wrap(~variable, scales = "free_x") + geom_vline(data = c, aes(xintercept = truth.alpha), color = "red")

```

A plot of the p values for BUSTED versus BUSTED-SRV. THis allows us to compare the results of the two analysis to each other. 

```{r p plot YesYes}
YesYes.process.dat%>% ggplot(aes(x= BUSTED.P,y=BUSTED.SRV.P))+geom_point()+geom_vline(xintercept = 0.05,color="red")+geom_hline(yintercept = 0.05, color = 'red')
```

*************************

#Yes No data
```{r YesNo data set-up, echo=FALSE}

YesNo.dat=read.csv("G:/BRC/SimResults/Five_seq/YesNo_results.csv",  as.is = T)
#YesNo.brlen = branch_length("G:/BRC/SimResults/YesNo/")
YesNo.process.dat = process.dat(YesNo.dat)
YesNo.melt.dat=melt(YesNo.process.dat[,c(1,31:35)])
YesNo.sum.stat = box.sum.stats(YesNo.process.dat)
YesNo.bias = YesNo.dat[,c(1,17:18,21:22,4:5)]

```







```{r set up truth table YesNo, echo=FALSE}

truth.YesNo = matrix(c(1,1,1,0.1,0.5,7,0.333,0.333,0.3337000000000001,0.5,0.3,0.2),nrow = 6, ncol= 2)
colnames(truth.YesNo)= c(" True Rates", "True Weights")
rownames(truth.YesNo) = c("alpha 1","alpha 2","alpha 3", "omega 1", "omega 2", "omega 3")
```



```{r summary stats table YesNo, echo = FALSE}
true.omegas.rates = c(truth.YesNo[4,1],truth.YesNo[4,1],truth.YesNo[5,1],truth.YesNo[5,1],truth.YesNo[6,1],truth.YesNo[6,1])

sum.table.omegas =gen.summary.o.tabs(YesNo.process.dat)[,3:4] %>% cbind("True Rates" = true.omegas.rates) %>% cbind("Estimated Weight" = cbind( YesNo.dat$BUSTED.omega1.prop, YesNo.dat$BUSTED.SRV.omega1.prop,YesNo.dat$BUSTED.omega2.prop,YesNo.dat$BUSTED.SRV.omega2.prop,YesNo.dat$BUSTED.omega3.prop,YesNo.dat$BUSTED.SRV.omega3.prop)  %>% apply(2,mean)) %>% cbind("True Weights" =c(truth.YesNo[4,2],truth.YesNo[4,2],truth.YesNo[5,2],truth.YesNo[5,2], truth.YesNo[6,2], truth.YesNo[6,2]))

sum.table.alphas = gen.summary.a.tabs(YesNo.process.dat)[,3:4] %>% cbind("True Rates"=c(truth.YesNo[1:3,1])) %>% cbind("Estimates Weight"=cbind(YesNo.process.dat$SRV.alpha1.prop,YesNo.process.dat$SRV.alpha2.prop,YesNo.process.dat$SRV.alpha3.prop) %>% apply(2,mean)) %>% cbind("True Weights" = truth.YesNo[1:3,2])

sum.table = rbind(sum.table.omegas,sum.table.alphas)
```

`r kable(sum.table,"markdown")`

Here we can see that the mean estimated omega3 value `r sum.table.omegas[5,2]` which is wildly over the true value of 1. This is what we'd expect to see as BUSTED does not account for synonymous rate variation and we simulated with a SRV and a high alpha 3 rate. 

```{r, echo = FALSE}

q = cbind("Truth"=as.numeric(sum.table[1:6,3]),variable=c("BUSTED.omega1.MLE","BUSTED.SRV.omega1.MLE","BUSTED.omega2.MLE","BUSTED.SRV.omega2.MLE","BUSTED.omega3.MLE", "BUSTED.SRV.omega3.MLE")) %>% as.data.frame()
q$Truth = as.numeric(sum.table[1:6,3])
YesNo.bias %>% melt() %>% ggplot(aes(value))+geom_histogram() +facet_wrap(~variable, scales = "free", ncol = 2)+ geom_vline(data = q,aes(xintercept = as.numeric(Truth)),color = "red") + ggtitle("Distribution of Omega R")

```

The histograms below show the distribution of the alpha rates

```{r histograms YesNo, echo = F, warning=F}
truth.alpha=c(truth.YesNo[1:3,1])
c = cbind(as.numeric(truth.alpha),variable=c("true.alpha1","true.alpha2","true.alpha3")) %>% as.data.frame()
ggplot(YesNo.melt.dat, aes(value))+geom_histogram()+facet_wrap(~variable, scales = "free_x") + geom_vline(data = c, aes(xintercept = truth.alpha), color = "red")

```

A plot of the p values for BUSTED versus BUSTED-SRV. THis allows us to compare the results of the two analysis to each other. 

```{r p plot YesNo}
YesNo.process.dat%>% ggplot(aes(x= BUSTED.P,y=BUSTED.SRV.P))+geom_point()+geom_vline(xintercept = 0.05,color="red")+geom_hline(yintercept = 0.05, color = 'red')
```


**********************************************

#Combining the simulation results

```{r combine into data frame, echo=FALSE}
  all.dat =bind_rows(NoNo.dat.no.outs,YesNo.process.dat,YesYes.process.dat,NoYes.process.dat)
```

```{r p plot of all, echo = FALSE}
all.dat %>% ggplot(aes(x= BUSTED.P,y=BUSTED.SRV.P))+geom_point()+geom_vline(xintercept = 0.05,color="red")+geom_hline(yintercept = 0.05, color = 'red')
```

```{r}
all.dat %>% group_by(p.cat,p.srv.cat)%>% select(contains("true"))%>% melt() %>% ggplot(aes(x = variable, y = value))+geom_boxplot(aes(color=interaction(p.cat,p.srv.cat)))+coord_flip(ylim = c(0,10))
```

```{r}
all.dat %>% group_by(p.cat,p.srv.cat)%>% select(matches("*omega\\d.MLE"))%>% melt() %>% ggplot(aes(value))+geom_histogram(aes(fill=interaction(p.cat,p.srv.cat)))+ facet_wrap(~variable, scales = "free", ncol = 2)
```





